%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    urlcolor=cyan           % color of external links
}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Sean McQueen} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

2109 5th Ave \hfill \href{mailto:sean@mcqueen.net}{sean@mcqueen.net} \\
Seattle, WA 98121  \hfill \href{https://www.linkedin.com/in/snmcqueen}{LinkedIn} \\
(206) 718 - 7746 \hfill \href{http://facebook.com/sean.mcqueen}{Facebook}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{SUMMARY}

Software Engineer with 3 years of iOS and web development experience. Experienced managing projects and leading small teams.

%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelors,} Computer Science \& Economics \hfill 2013 \\
Claremont McKenna College, Claremont, CA

%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Vagabond} \hfill May 2016 - August 2016 \\
Solo backpacking in many countries in Europe.

{\sl Software Engineer} \hfill January 2014 - May 2016 \\
\href{http://www.nextdoor.com}{Nextdoor}, San Francisco, CA \\
Nextdoor is a hyperlocal social platform for neighbors. I joined the company as the 25th engineer. During my time at Nextdoor I was involved with backend infrastructure for the newsfeed and user-facing iOS inititives. \\
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Learned Objective-C and the iOS platform while on a deadline to ship code: I implemented multiple photo uploading and viewing for neighbor posts on iOS and the web in summer 2014. Handled limited server thread capacity by uploading photos directly to AWS S3. Increased number of photo posts by neighbors by over 100\%.
\item Led a cross-platform team of 7 engineers (web, iOS \& Android) to build the 2014 Holiday Cheer Map, a user growth inititive. Worked with designers and PM to spec the feature and plan for launch. Responsible for negotiating and then hitting aggressive development deadlines. Increased user sign-up during the slow holiday season by 16,000 users.
\item Led iOS development of Nextdoor Now's MVP (\"Nextdoor Babysitting\") with a team of 2 other iOS engineers over a 4 month period."
\item Developed our 2015 Engineering Intern program. Interviewed dozens of intern candidates during the hiring process. Ran an onboarding process for interns that included talks by key employees. Helped plan social events (including lunch talks with Nextdoor executives and founders).
\item Refactored Ads backend to increase developer productivity. Helped build the initial iOS advertising product at Nextdoor.
\end{itemize}

{\sl Software Engineering Intern} \hfill Summer 2013 \\
\href{http://www.nextdoor.com}{Nextdoor}, San Francisco, CA
\begin{itemize}
\item Joined the Infrastructure team and helped write the interface to a new asynchronous backend newsfeed service that served content to the main Django application. This project sped up newsfeed load times by 2X and gave us way more headroom.
\end{itemize}

{\sl Managing Editor} \hfill March 2012 - March 2013 \\
\href{http://cmcforum.com/}{CMC Forum}, Claremont, CA
\begin{itemize}
\item Worked with Editor in Chief to manage a staff of 30 for a daily online publication with 30,000 pageviews a month. Managed a publishing schedule, a team of editors and the site's social media presence.
\end{itemize}

{\sl Product Management Intern} \hfill Summer 2012 \\
\href{https://www.atlassian.com/}{Atlassian}, Sydney, Australia
\begin{itemize}
\item Shipped a JavaScript charting plugin for Confluence (wiki software) with 4 other interns. Alternatively acted as UX designer, project manager and CSS lackey.
\end{itemize}

%----------------------------------------------------------------------------------------

\section{LANGUAGES \\ AND \\ TECH}
{\bf Comfortable:} Objective-C, iOS SDK and APIs (versions 7-9), XCode, Python, Django, Git \\
{\bf Experienced:} Swift, JavaScript, Postgres, HTML, CSS, SASS, Thrift RPC, LaTeX \\
{\bf Familiar:} iOS Instruments, Java, Go, C++, Ruby, Bash \\

%----------------------------------------------------------------------------------------

\section{INTERESTS}
{\sl ]Travel:} I have been to many countries in the world and I'm often planning another trip! \\
{\sl Improv:} I took improv classes and performed in front of live audiences in San Francisco for the past year. I'm a comedy and live theatre fan; I'm looking forward to the improv scene in NYC.  \\
{\sl Reading:} \href{http://www.goodreads.com/user/show/55900995-sean-mcqueen}{See what books I'm reading currently} \\

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}