
% I've stolen this LaTeX resume template from the Internet. The file res.cls contains the
% original copywrite information. Look there! I cleaned this up, changed it a ton
% and removed the copywrite information because it was getting in my way...
%  -- Sean

%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res}

\usepackage{helvet}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=cyan
}

\setlength{\textwidth}{5.1in}

\begin{document}

%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\bf Sean McQueen}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
New York, NY | 206-718-7746 | \href{mailto:sean@mcqueen.net}{sean@mcqueen.net} | \href{https://www.linkedin.com/in/snmcqueen}{Linkedin}

%----------------------------------------------------------------------------------------

\begin{resume}
\begin{flushleft}  % Force text to be left aligned

\section{SUMMARY}

Software Engineer with 3 years of experience. Experienced building high scale backend systems and high quality frontend experiences. Looking to build great products.

%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Software Engineer} \hfill November 2016 - present \\
\href{http://www.beeswax.com}{Beeswax}, New York, NY \\
We build programmatic ad bidding infrastructure as a service. I joined the company as the 14th employee.
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Refactored Python services for processing large amounts of customer data, reducing error rates and increasing reliability.
\item Implemented a Hadoop cluster for data analysis using AWS's Elastic Map Reduce. Designed the cluster so that it runs Hadoop collocated with Aerospike and gets continuous replicated data from our production key-value store allowing for low-networking distributed data scans. Reduced scan times from 48 hours to under 2 hours.
\item Initiated and managed the transition for our oncall rotation from reliance on automated Slack messages to Pagerduty alerts, encouraging better oncall practices.
\item Maintain multi-threaded Python services that run on AWS's EC2 Container Service.
\end{itemize}

{\sl Software Engineer} \hfill January 2014 - May 2016 \\
\href{http://www.nextdoor.com}{Nextdoor}, San Francisco, CA \\
Nextdoor is a social platform for neighbors.
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Implemented the first ads selection algorithm at Nextdoor. Built and enhanced tools to support advertising sales. Helped build our initial iOS advertising product.
\item Led iOS development of Nextdoor Babysitting -- an early prototype of a neighbor-to-neighbor services product. Worked with a team of 2 other iOS engineers over a 4 month period.
\item Led a cross-platform team of 7 engineers (web, iOS \& Android) to build the 2014 Holiday Cheer Map, a neighbor-sourced map of holiday related points of interest. Worked with designers and product manager to spec the feature and plan for launch. Responsible for negotiating and then hitting aggressive development deadlines. Increased user sign-up during the slow holiday season by 16,000 users.
\item Implemented multiple photo uploading and viewing for neighbor posts on iOS and the web. Handled limited server thread capacity by uploading photos directly to AWS S3. Increased number of photo posts by neighbors by over 100\% and number of photos on the platform by over 500\%.
\end{itemize}

{\sl Software Engineering Intern} \hfill Summer 2013 \\
\href{http://www.nextdoor.com}{Nextdoor}, San Francisco, CA
\begin{itemize}
\item Joined the infrastructure team and helped write the client library to a backend newsfeed content service. The new service was multi-threaded and stateless, giving us horizontal scalability that reduced server costs and allowed us to optimize our newsfeed load times, leading to a 2X speed up on our most important pages.
\end{itemize}

{\sl Managing Editor} \hfill March 2012 - March 2013 \\
\href{http://cmcforum.com/}{CMC Forum}, Claremont, CA
\begin{itemize}
\item Worked with the Editor-in-Chief to manage a staff of 30 for a daily online publication with 30,000 pageviews a month. Managed a publishing schedule, a team of editors and the site's social media presence.
\end{itemize}

{\sl Product Management Intern} \hfill Summer 2012 \\
\href{https://www.atlassian.com/}{Atlassian}, Sydney, Australia
\begin{itemize}
\item Shipped a charting plugin for Confluence (wiki software) with 4 other interns. Acted as UX designer, project manager and frontend developer.
\end{itemize}

%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelors,} Computer Science \& Economics (dual major) \hfill 2013 \\
Claremont McKenna College, Claremont, CA
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Senior Thesis: \href{https://github.com/s-mcqueen/js_and_politics/blob/master/final_draft/FINAL.pdf}{JavaScript and Politics: How a Toy Language Took Over the World}
\item Activities: Claremont Coders Club (co-founder), Washington Semester Program, 5C Hackathon (Fall 2012, Spring 2013, Fall 2013)
\end{itemize}

%----------------------------------------------------------------------------------------

\section{LANGUAGES \\ \& TECH }
{\sl Very comfortable with...} \\
\hskip2em Python, AWS, Docker, Protocol Buffers, Objective-C, iOS, Postgres, Aerospike \\
{\sl Have written production code using...} \\
\hskip2em C++, Java, Bash, Javascript, MySQL \\
{\sl Some familiarity with...}\\
\hskip2em Go, React \\


%----------------------------------------------------------------------------------------
\end{flushleft}

\end{resume}
\end{document}
